---
title: "HW for tuesday 9/10"
output: html_document
date: "2023-01-12"
editor_options: 
  markdown: 
    wrap: 72
---

```{r}
library(openintro)
library(tidyverse)
library(ggplot2)
```

#\> ── Attaching packages ───────────────────────────────────────
tidyverse 1.3.2 ── #\> ✔ ggplot2 3.4.0 ✔ purrr 0.3.5 #\> ✔ tibble 3.1.8
✔ dplyr 1.0.10 #\> ✔ tidyr 1.2.1 ✔ stringr 1.4.1 #\> ✔ readr 2.1.3 ✔
forcats 0.5.2 #\> ── Conflicts
────────────────────────────────────────── tidyverse_conflicts() ── #\>
✖ dplyr::filter() masks stats::filter() #\> ✖ dplyr::lag() masks
stats::lag()

```{r }
ggplot(data = mpg) +  
  geom_point(mapping = aes(x = displ, y = hwy))
```

###3.3 exursize

```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```

1.Because the code needs to look like this: ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy), color = "blue")

2.  categorical is Model name, manufacturer name, year of manufacturer,
    fuel type, and type of drive train, type of transmission. The
    continuous variables are number of cylinders, city miles per gallon,
    and highway miles per gallon

```{r 3.3.3}
ggplot(data = mpg) +  
  geom_point(mapping = aes(x = displ, y = hwy,color= cty, size=fl ))
```

You cant put a continuous variable in shape, but size works with
continuous.

```{R}
ggplot(data = mpg) +  
  geom_point(mapping = aes(x = displ, y = hwy,color= hwy))
```

4.if you use the same variable for two aesthetics it will do both, in
the example above hwy is both y and color cause it to be darker with
less hwy. The color doesn't add any more information but rather looks
cool.

```{r 3.3.5}
ggplot(data = mpg) +  
  geom_point(mapping = aes(x = displ, y = hwy,size= cty, stroke=2), color="blue",shape=2)
```

5.  Stroke controls the size of the outline

```{r 3.3.6}
ggplot(data = mpg) +  
  geom_point(mapping = aes(x = displ, y = hwy,size= cty, color=displ < 5), shape=2)
```

6.  it make the point that has displ less than 5 a different color, with
    the color answering the question of what points have displ \<5

###3.5 extrusize

``` {r3.5.1}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = hwy))
facet_grid(drv ~ cyl)
```

1.  it puts all the dots on one line, shows the highway speed for 4
    wheel drive, front wheel, and rear wheel. this data would be good to
    find out what wheel drive is the fastest.

```{r 3.5.2}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = drv, y = cyl))
```

2.  this tells you how many cylinders each wheel drive could have, it
    has useful data that says 4 wheel and rear wheel engines cant have
    certain cylinder engines while front wheel has more diversity in
    cylinder numbers

```{r 3.5.3}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(drv ~ .)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) +
  facet_grid(. ~ cyl)
```

3.  it makes separate graphs for each driver train so you can just
    compare within drive train.

```{r 3.5.4}
  ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy)) + 
  facet_wrap(~ class, nrow = 4)
```

4.it is easier to compare categorical variables like car type or drive
train, but its harder to compare across section since they all have
there own graph.

5.  Nrow is number of rows

6.If you have a vairibale that has HWY being very drastic you would want
to be able to better see the difference because it gives them more room
on the y axis.

###3.6 exursize

1.line chart: C+Geom_freqpoly(), BoxPlot: F+Geom_boxplot(), Histogram:
c+geom_histogram()

2.  it is going to be a point chart with a smooth line over it, and the
    drv color will make different color dots and 3 smooth lines.

```{r 3.6.2}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = drv)) + 
  geom_point() + 
  geom_smooth(se = FALSE)
```

3.Show legend = false gets rid of the grey outline around the smooth
lines, and the grey part is there too show that there is a range of
possible points around the smoothed line.

4. SE means show legend, so if it is false then it say don't show legend

```{r 3.6.5}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_point() + 
  geom_smooth()

ggplot() + 
  geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) + 
  geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))
```

