---
title: "Visualizing Starwars characters"
author: "Mine Çetinkaya-Rundel"
format: html
editor: visual
---

```{r}
#| label: load-packages
#| include: false

library(tidyverse)
library(ggplot2)
```

1.  Glimpse at the starwars data frame.

```{r}
#| label: glimpse-starwars

glimpse(starwars)
```

2.  Modify the following plot to change the color of all points to `"pink"`.

```{r}
#| label: scatterplot

ggplot(starwars, 
       aes(x = height, y = mass, color = gender, size = birth_year)) +
  geom_point(color = 'pink')
```

3.  Add labels for title, x and y axes, and size of points. Uncomment to see the effect.

```{r}
#| label: scatterplot-labels

ggplot(starwars, 
       aes(x = height, y = mass, color = gender, size = birth_year)) +
  geom_point(color = "#30509C") +
  labs(
    #title = "starwars",
    #x = "height", 
    #y = "mass",
    # birth_year
    )
```

4.  Pick a single numerical variable and make a histogram of it. Select a reasonable binwidth for it.

(A little bit of starter code is provided below, and the code chunk is set to not be evaluated with `eval: false` because the current code in there is not valid code and hence the document wouldn't knit. Once you replace the code with valid code, set the chunk option to `eval: true`, or remove the `eval` option altogether since it's set to `true` by default.)

```{r}
#| label: histogram
#| eval: true

ggplot(starwars, aes(x= birth_year)) +
  geom_histogram(binwidth = 5 )
```

5.  Pick a numerical variable and a categorical variable and make a visualization (you pick the type!) to visualization the relationship between the two variables. Along with your code and output, provide an interpretation of the visualization.

```{r}
#| label: num-cat
ggplot(starwars, aes(x=skin_color,y=mass))+
geom_point() 

```

Interpretation goes here...

6.  Pick a single categorical variable from the data set and make a bar plot of its distribution.

```{r}
#| label: barplot
ggplot(starwars) +
geom_bar(aes(hair_color))
```

7.  Pick two categorical variables and make a visualization to visualize the relationship between the two variables. Along with your code and output, provide an interpretation of the visualization.

```{r}
#| label: cat-cat
ggplot(starwars, aes(x=gender, y=hair_color))+
  geom_point()

```

only masculine people have blond hair, and only feminine have auburn but aurburn grey is only in masculine people.

8.  Pick two numerical variables and two categorical variables and make a visualization that incorporates all of them and provide an interpretation with your answer.

(This time no starter code is provided, you're on your own!)

```{r}
#| label: multi
ggplot(starwars, aes(x=height, y= birth_year, shape=gender, color=sex))+
  geom_point()

```

the shortest is the oldest, there is no correlation between age and height, it does seem all female sex and feminine gender are around the same age and height. there is a clear average age and height that majority of character fall into: birth year (0-125) and height (150-200)
